POMDP comparisons across sigma_m, sigma_g

### 2017-10-07 appendix/appendixB.Rmd

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 3) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(id = "pomdp_historical", 
                             model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")

>>>>

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 4) # Reserve ~ 10 GB per core
log_dir <- "pomdp_historical"
```

@@

## POMDP solution (slow, >20,000 seconds per loop memory intensive)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = meta[i, "r"][[1]], 
                             K = meta[i, "K"][[1]], 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal")
